---
title: "Assignment 2"
author: "Alondra Hidalgo Morales"
date:  "`r format(Sys.time(), '%Y-%b-%d, %I:%M %p')`"
---



 
```{r}
library(dplyr)
library(gapminder)
```
```{r}
data(gapminder)
head(gapminder)
```

##### **Q1. What class is the gapminder dataset?**

```{r}
class(gapminder)
```
##### **Q2. Filter a section of gapminder with a life expectancy smaller than 29.**
```{r}
gapminder |> 
  filter(lifeExp < 29)
```

##### **Q3. Filter the dataset for the country Rwanda and for years greater than 1979.**
```{r}
gapminder |> 
  filter(country == "Rwanda", year > 1979)
```

##### **Q4. Create a new dataset from gapminder excluding the column gdpPercap**
```{r}
gapminder |> 
  select(country, continent, year, lifeExp, pop)
```

##### **Q5 Arrange the dataset in ascending order of lifeExp.**
```{r}
gapminder |> 
  arrange(lifeExp)
```

##### **Q6. Arrange the dataset in descending order of lifeExp**
```{r}
gapminder |> 
  arrange(desc(lifeExp))
```

##### **Q7. Create a new dataset with only the columns year and lifeExp.**
```{r}
new_dataset <- gapminder |> 
  select(year, lifeExp)
new_dataset
```

##### **Q8. Filter the dataset for the country Cambodia and show only the columns year and lifeExp.**
```{r}
gapminder |> 
  filter(country == "Cambodia") |> 
  select(year, lifeExp)
```
##### **Q9. Select only the countries in Africa.**
```{r}
gapminder |> 
  filter(continent == "Africa")
```
##### **Q10. Create a new column called lifeExp_months that shows life expectancy in months.**
```{r}
gapminder |> 
  mutate(lifeExp_months = lifeExp * 12)
```

