---
title: "Assignment 3"
author: "Alondra Hidalgo Morales"
date:  "`r format(Sys.time(), '%Y-%b-%d, %I:%M %p')`"
---
```{r}
library(ggplot2)
```
```{r}
data("trees")
head(trees)
```

##### **Q1. Create a histogram showing the distribution of Girth**

```{r}
hist(trees$Girth)
```

##### **Q2. Create a histogram showing the distribution of Volume.**
```{r}
hist(trees$Volume,
     main = "Distribution of volume",
     xlab = "Volume")
```

##### **Q3. Create a scatterplot showing the relationship between Girth and Volume.**
```{r}
plot(trees$Girth, trees$Volume,
     main = "Girth vs. Volume",
     xlab = "Girth",
     ylab = "Volume")
```

##### **Q4. Use the Shapiro–Wilk test to assess whether Volume is normally distributed. Report the p-value and state whether the data are normally distributed.**
```{r}
shapiro.test(trees$Volume)
```

###### The Shapiro-Wilk test gave a p-value of 0.003579. Since the p- value is less than 0.05 we reject the null hypothesis.Volume is not normally distributed

##### **Q5. Repeat the Shapiro–Wilk test for Girth. Report the p-value and state whether Girth is normally distributed.**
```{r}
shapiro.test(trees$Girth)
```

###### The Shapiro-Wilk test gave a p-value of 0.08893. Since the p- value is greater than 0.05 we fail to reject the null hypothesis. Girth is normally distributed. 
